### 2017-07-21 mlppi-ksii17/cover-letter.tex
Submission

\item Experiments: we provide additional runtime statistics measured from our experiments, as exhibited in {\color{blue}Table~1} on page~16. In addition, we compare the recommendation quality of our tool with those of a human expert and a vanilla approach (no partitioning), as shown in {\color{blue}Fig.~5} on page~17.

>>>>

\item Experiments: we provide additional runtime statistics measured from our experiments, as exhibited in {\color{blue}Table~1} on page~16. In addition, we compare the recommendation quality of our tool with those of a human expert and a vanilla approach (no partitioning), as shown in {\color{blue}Fig.~5~(b)} on page~17.
